---
title: "Assignment 5"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Author: Ray Wu

## Bringing in Rectangular data

First, we load the `gapminder` and `tidyverse` packages: 

```{r}
library(gapminder)
library(tidyverse)
```
## Factor Management

### Drop Oceania

```{r}
gapminder %>% 
  str()
```

```{r}
gapminder %>% 
  filter(continent != 'Oceania') %>% 
  droplevels() %>% 
  str()
```

```{r}
gapminder_2007 = gapminder %>% 
  filter(year == 2007)
```

```{r}
gapminder_2007 %>% 
  mutate(continent=fct_reorder(continent,gdpPercap,min))
```


## file i/o

### write_csv()/read_csv()
```{r}
write_csv(gapminder_2007, 'gapminder_2007.csv')
```

confirm that the file exists:
```{r}
list.files()
```
We see that the file `gapminder_2007.csv` exists so we know that `write_csv` worked as intended

```{r}
read_data = read_csv('gapminder_2007.csv')

read_data %>% str()
```

### saveRDS()/readRDS()

```{r}
gapminder_2007 %>% saveRDS('gapminder_2007.rds')
```

Check to make sure that the file exists: 

```{r}
list.files()
```

Now, read in the file again: 

```{r}
rds_file = readRDS('gapminder_2007.rds')
```

As expected, we do not encounter any problems with reading in the `.rds` file

